---
title: "coagglomeration -- interplots -- with manufacturing and services separately"
output: html_notebook
---

by sandorjuhasz

### coagglomeration

setting info



```{r, echo=FALSE, results=FALSE, message=FALSE}
library(data.table)
library(dplyr)
library(stargazer)
library(ivreg)
library(lmtest)
library(sandwich)
library(interplot)
library(cowplot)
source("../code/05a_regression_functions.R")

# parameters
focal_year <- 2017
#region_level <- "nuts3"
region_level <- "nuts4"
#region_level <- "city"
version <- ""

```



**Currently in the main text**

```{r, echo=FALSE, warning=FALSE}
### --- Figure 2 -- interplots
fontsize <- 10
region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)
#reg_df <- reg_df[complete.cases(reg_df[ , c("io_norm2")]), ]


# the model -- EGK
int_egk <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = reg_df)

ip_a <- interplot(m = int_egk,
                 var1 = "sr_norm",
                 var2 = "io_wiot_hun",
                 #var2 = "io_norm3",
                 size = 3,
                 xmin = -1,
                 xmax = 1,
                 rfill = "#15636A") +
  xlab("IO (WIOD)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.025, 0.35) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))
  #theme(plot.margin = unit(c(2, 1, 0, 1), "cm"))

ip_b <- interplot(m = int_egk,
                 var1 = "io_wiot_hun",
                 #var1 = "io_norm3",
                 var2 = "sr_norm",
                 size = 3,
                 xmin = -1,
                 xmax = 1,
                 rfill = "#15636A") +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (WIOD)") +
  ylim(-0.025, 0.35) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))
  #theme(plot.margin = unit(c(2, 1, 0, 1), "cm"))


# the model -- LC (emp)
#int_pemp <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = reg_df)
int_pemp <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = reg_df)

ip_c <- interplot(m = int_pemp,
                  var1 = "sr_norm",
                  var2 = "io_wiot_hun",
                  #var2 = "io_norm3",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A") +
  xlab("IO (WIOD)") +
  ylab("Coeff. labor (SR)") +
  ylim(0, 0.7) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))
  #theme(plot.margin = unit(c(2, 1.5, 0, 1), "cm"))

ip_d <- interplot(m = int_pemp,
                  var1 = "io_wiot_hun",
                  #var1 = "io_norm3",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A") +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (WIOD)") +
  ylim(0, 0.7) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))
  #theme(plot.margin = unit(c(2, 1.5, 0, 1), "cm"))


# combine subplots
subplots1 <- plot_grid(
  ip_a, ip_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)
subplots2 <- plot_grid(
  ip_c, ip_d,
  #labels = c("C", "D"), label_size = fontsize,
  ncol = 2
)


# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (EGK)", fontface="bold", size = fontsize)
plot_title2 <- ggdraw() + draw_label("Coagglomeration (LC)", fontface="bold", size = fontsize)


# combined version
plot_grid(plot_title1, subplots1, plot_title2, subplots2, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))
```


**LC coagglomeration with IO (trans) NUTS4 -- best looking**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
#region_codes <- c("nuts3")
region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_norm3",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_norm3",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
#int_prca_manuf <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
#int_prca_serv <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (transactions)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.9) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (transactions)") +
  ylim(-0.1, 0.9) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (LC)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```




**LC coagglomeration with IO (trans) NUTS3**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
region_codes <- c("nuts3")
#region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_norm3",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_norm3",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
#int_prca_manuf <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
#int_prca_serv <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (transactions)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.9) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (transactions)") +
  ylim(-0.1, 0.9) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (LC)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```



**EGK coagglomeration with IO (trans) NUTS4**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
#region_codes <- c("nuts3")
region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


#int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_norm3",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_norm3",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
#int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
int_prca_manuf <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
#int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
int_prca_serv <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (transactions)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (transactions)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (EGK)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```




**EGK coagglomeration with IO (trans) NUTS3**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
region_codes <- c("nuts3")
#region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


#int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_norm3",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_norm3",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
#int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
int_prca_manuf <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
#int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
int_prca_serv <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_norm3", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_norm3", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (transactions)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (transactions)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (EGK)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```




**LC coagglomeration with IO (WIOD) NUTS4**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
#region_codes <- c("nuts3")
region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


#int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = reg_df)
int_prca <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_wiot_hun",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_wiot_hun",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
#int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
#int_prca_manuf <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = manuf_df)
int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
#int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
#int_prca_serv <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = services_df)
int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (WIOD)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (WIOD)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (LC)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```




**LC coagglomeration with IO (WIOD) NUTS3**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
region_codes <- c("nuts3")
#region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


#int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = reg_df)
int_prca <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_wiot_hun",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_wiot_hun",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
#int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
#int_prca_manuf <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = manuf_df)
int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
#int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
#int_prca_serv <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = services_df)
int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_wiot_hun * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (WIOD)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (WIOD)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (LC)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```





**EGK coagglomeration with IO (WIOD) NUTS4**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
#region_codes <- c("nuts3")
region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


#int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
int_prca <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_wiot_hun",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_wiot_hun",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
#int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
int_prca_manuf <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
#int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
int_prca_serv <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (WIOD)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (WIOD)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (EGK)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```




**EGK coagglomeration with IO (WIOD) NUTS3**

```{r, echo=FALSE, warning=FALSE}
fontsize <- 10
version <- ""
region_codes <- c("nuts3")
#region_codes <- c("nuts4")
model_version <- c("noFE", "FE")
path <- paste0("../data/oc15_2023_dec/04oc_data_", version, region_codes, "_", focal_year, ".csv")
reg_df <- prep_baseline_regression_table(path)

# filter for manufacturing and services only
manuf <- c(10, 34)
manuf_df <- subset(
  reg_df,
  (ind1_2d >= manuf[1]) &
    (ind1_2d < manuf[2]) &
    (ind2_2d >= manuf[1]) &
    (ind2_2d < manuf[2])
)

services <- c(49, 89)
services_df <- subset(
  reg_df,
  (ind1_2d >= services[1]) &
    (ind1_2d < services[2]) &
    (ind2_2d >= services[1]) &
    (ind2_2d < services[2])
)


#int_prca <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = reg_df)
#int_prca <- lm(egk_coagg_stand ~ io_norm3 * sr_norm, data = reg_df)
int_prca <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = reg_df)
ip_a <- interplot(m = int_prca,
                  var1 = "sr_norm",
                  var2 = "io_wiot_hun",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

ip_b <- interplot(m = int_prca,
                  var1 = "io_wiot_hun",
                  var2 = "sr_norm",
                  size = 3,
                  xmin = -1,
                  xmax = 1,
                  rfill = "#15636A")

x_coords_main_a <- ggplot_build(ip_a)$data[[1]]$x
y_coords_main_a <- ggplot_build(ip_a)$data[[1]]$y
x_coords_main_b <- ggplot_build(ip_b)$data[[1]]$x
y_coords_main_b <- ggplot_build(ip_b)$data[[1]]$y



# manufacturing coords
#int_prca_manuf <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = manuf_df)
int_prca_manuf <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = manuf_df)

ip_manuf_a <- interplot(m = int_prca_manuf, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$x
y_coords_manuf_a <- ggplot_build(ip_manuf_a)$data[[1]]$y


ip_manuf_b <- interplot(m = int_prca_manuf, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$x
y_coords_manuf_b <- ggplot_build(ip_manuf_b)$data[[1]]$y




# services coords
#int_prca_serv <- lm(coagg_porter_rca01_stand ~ io_norm3 * sr_norm, data = services_df)
int_prca_serv <- lm(egk_coagg_stand ~ io_wiot_hun * sr_norm, data = services_df)

ip_serv_a <- interplot(m = int_prca_serv, var1 = "sr_norm", var2 = "io_wiot_hun", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$x
y_coords_serv_a <- ggplot_build(ip_serv_a)$data[[1]]$y


ip_serv_b <- interplot(m = int_prca_serv, var1 = "io_wiot_hun", var2 = "sr_norm", size=3, xmin = -1, xmax = 1,  rfill = "Black") +
  aes(color = "") +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  xlim(-1, 1) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=25)) +
  theme(plot.margin = unit(c(2, 1, 0, 1), "cm")) +
  guides(fill="none") +
  theme(legend.position="none")

x_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$x
y_coords_serv_b <- ggplot_build(ip_serv_b)$data[[1]]$y



int_ms_a <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_a, y = y_coords_manuf_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_a, y = y_coords_serv_a), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_a, y = y_coords_main_a), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.225, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("IO (WIOD)") +
  ylab("Coeff. labor (SR)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))

int_ms_b <- ggplot() +
  geom_line(data = data.frame(x = x_coords_manuf_b, y = y_coords_manuf_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_serv_b, y = y_coords_serv_b), aes(x, y), size = 2, color = "grey") +
  geom_line(data = data.frame(x = x_coords_main_b, y = y_coords_main_b), aes(x, y), size = 4, color = "#15636A") +
  #annotate("text", x = 0.5, y = 0.115, label = "Manufacturing", color = "black", size=10) +
  #annotate("text", x = 0.435, y = 0.85, label = "Services", color = "black", size=10) +
  xlab("Labor (SR)") +
  ylab("Coeff. IO (WIOD)") +
  ylim(-0.1, 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", size=1.5) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=fontsize-5), axis.title=element_text(size=fontsize))



# combine subplots
subplots1 <- plot_grid(
  int_ms_a, int_ms_b,
  #labels = c("A", "B"), label_size = fontsize,
  ncol = 2
)

# titles
plot_title1 <- ggdraw() + draw_label("Coagglomeration (EGK)", fontface="bold", size = fontsize)

# combined version
plot_grid(plot_title1, subplots1, ncol=1, rel_heights=c(0.1, 1, 0.1, 1))

```



