---
title: "OPTEN coagglomeration and MNEs"
output: html_notebook
---

developed by sandorjuhasz

### coagglomeration

```{r}
# results=FALSE, message=FALSE
source("../scripts/function_collection.R")
library(data.table)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(mefa4)
library(ggplot2)
library(ggraph)
library(patchwork)
library(cowplot)


# OPTEN data
firm_info <- fread("../data/opten-dataset/mta_cegalap.csv", encoding='Latin-1')

# geo categories
geo_data <- fread("../data/iranyitoszamok_BE.csv")

# transaction data
tr_df <- fread("../data/industry_industry_table_nace3d.csv", sep=";")

# key parameters
colors <- c("#e9c46a", "#264653")
region_col <- "jaras"
industry_col <- "nace3d"
indreg_grouper <- c(industry_col, region_col)

```


**Less than 5 digit NACE codes seem to be incorrect**

made corrections after manually checking 'fotev_nev' and 'fotev_kod'

```{r}
# generate 3-digit NACE codes -- NO leading zeros and many NAs
firm_info <- subset(firm_info, is.na(fotev_kod)==0)
firm_info$nace3d <- ifelse(nchar(firm_info$fotev_kod)==5,
                           as.numeric(substr(firm_info$fotev_kod, 1, 3)),
                           as.numeric(substr(firm_info$fotev_kod, 1, 2)))

# companies dataframe with key columns
cdf <- firm_info %>%
  select(oo_cegj_sz, hely, irsz, nace3d, letszam_besz18) %>%
  subset(is.na(irsz) == 0 & is.na(nace3d) == 0 & nace3d > 9) %>%
  subset(letszam_besz18 >= 2) %>%
  dplyr::rename(emp = letszam_besz18) %>%
  data.table()

# join location infos
cdf <- merge(
  cdf,
  unique(select(geo_data, irsz, jaras, megye)),
  by = "irsz",
  all.x = TRUE,
  all.y = FALSE) %>%
  subset(is.na(jaras) == 0)

# add industry, region and industry-region level attributes for future filters
cdf <- cdf %>%
  group_by_at(indreg_grouper) %>%
  mutate(nr_firms_indreg = n_distinct(oo_cegj_sz),
         total_emp_indreg = sum(emp)) %>%
  group_by_at(industry_col) %>%
  mutate(nr_firms_ind = n_distinct(oo_cegj_sz),
         total_emp_ind = sum(emp),
         nr_regions_ind = n_distinct(jaras)) %>%
  group_by_at(region_col) %>%
  mutate(nr_firms_reg = n_distinct(oo_cegj_sz),
         total_emp_reg = sum(emp),
         nr_ind_reg  = n_distinct(nace3d)) %>%
  data.table()

```


**Issue -- MAV / Tesco / other HUGE companies**

check plants table, hopefully we can filter out firms with 100+ plants


**FILTERS**

min 10 firms per industry-region -- AND -- min 2 regions per industry -- AND -- min 2 industries per region



```{r}
# coagglomeration table using filters
coagg_table <- construct_coagglomeration_table(cdf,
                                min_nr_firms_indreg = 10,
                                min_nr_regions_ind = 2,
                                min_nr_ind_reg = 2,
                                region_col,
                                industry_col)
```


```{r, warning=FALSE}
# coagglomeration plots
p1 <- ggplot(coagg_table, aes(x = coagglomeration)) +
  geom_histogram(bins=30, , color="black", fill=colors[2]) +
  xlab("Coagglomeration") +
  ylab("Frequency") +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

p2 <- ggplot(coagg_table, aes(x = coagglomeration)) +
  geom_histogram(bins=30, , color="black", fill=colors[2]) +
  xlab("Coagglomeration") +
  ylab("Frequency") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

(p1 + p2)
```

**coagglomeration issues**

237 : Cutting, shaping and finishing of stone\
383 : Materials recovery

663 : Fund management activities \
701 : Activities of head offices 

351 : Electric power generation, transmission and distribution \
822 : Activities of call centres 


```{r}
arrange(coagg_table, desc(coagglomeration))
```

```{r}
# EON service center w/ 1000+ employee -- 822 nace3d
# 
```



### transaction data


```{r}
# manipulation
tr_df$ind1 <- as.character(tr_df$ind1)
tr_df$ind2 <- as.character(tr_df$ind2)
#tr_df <- subset(tr_df, ind1 < ind2)

idf <- merge(
  coagg_table,
  select(tr_df, ind1, ind2, nr_trans),
  by = c("ind1", "ind2"),
  all.x = TRUE,
  all.y = FALSE
)

idf$log10_trans <- log10(idf$nr_trans)
idf$log10_trans[is.infinite(idf$log10_trans)] <- 0
idf$log10_trans[is.na(idf$log10_trans)] <- 0

```


```{r}
limited_idf <- subset(idf, nr_trans >= 5)

sc1 <- ggplot(idf, aes(x=coagglomeration, y=log10_trans)) +
  geom_point(size=5, color=colors[1], alpha=0.8) +
  #geom_smooth(method=lm, se=TRUE, linetype="dashed", color="black") +
  xlab("Coagglomeration") +
  ylab("Transactions (log)") +
  #ylim(0, 1800) +
  #scale_x_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  #scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

sc2 <- ggplot(limited_idf, aes(x=coagglomeration, y=log10_trans)) +
  geom_point(size=5, color=colors[1], alpha=0.8) +
  #geom_smooth(method=lm, se=TRUE, linetype="dashed", color="black") +
  xlab("Coagglomeration") +
  ylab("Transactions (min 5) (log)") +
  #ylim(0, 1800) +
  #scale_x_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  #scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

(sc1 + sc2)

print(cor(idf$coagglomeration, idf$log10_trans))
print(cor(limited_idf$coagglomeration, limited_idf$log10_trans))
```


### skill relatedness data



### MNEs

Following Bisztray et al. 2022 WP -- MNEs should be\
*10% foreign share*\
*min 500 employees*


OPTEN only have information on actual owners -- no foreign capital share\
*min 200 employees* \
*home country of the owner company*


```{r}
# MNE limit
mne_limit <- 100

# owner data from OPTEN
ownerdata <- fread("../data/opten-dataset/mta_tulaj.csv", encoding='Latin-1')

# owners are foreign firms
foreign_firm_owners <- ownerdata %>%
  subset((ceg_orsz != "") & (ceg_orsz != "HU")) %>%
  dplyr::select(oo_cegj_sz, ceg_orsz, ceg_varos) %>%
  data.table() %>%
  unique() %>%
  rename(country = ceg_orsz, city = ceg_varos)


# owners are foreign people -- NOT finished
foreign_person_owners <- ownerdata %>%
  subset((szemely_orsz != "") & (szemely_orsz != "HU")) %>%
  dplyr::select(oo_cegj_sz, szemely_orsz, szemely_varos) %>%
  data.table() %>%
  unique() %>%
  rename(country = szemely_orsz, city = szemely_varos)

foreign_table <- unique(rbind(foreign_firm_owners, foreign_person_owners))


# MNE dataframe
mne_df <- subset(cdf, emp >= 5)

mne_df <- merge(
  mne_df,
  foreign_table,
  by = "oo_cegj_sz",
  all.x = TRUE,
  all.y = FALSE
)
mne_df <- subset(mne_df, is.na(country) ==0)
mne_limited <- subset(mne_df, emp >= mne_limit)

```

```{r}
# plot modifications
mne_df$log10_emp <- log10(mne_df$emp)

# size of foreign firms
ggplot(mne_df,
  aes(x = log10_emp)) +
  xlab("Employment (log10)") +
  ylab("Frequency") +
  #xlim(0, 1500) +
  #ylim(0, 400) +
  geom_histogram(bins=30, color="black", fill=colors[1]) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=20), axis.title=element_text(size=25))

```


```{r}
# country distribution
country_distr <- mne_limited %>%
  group_by(country) %>%
  summarise(nr_firms = n_distinct(oo_cegj_sz)) %>%
  data.table()

ggplot(country_distr, aes(x=country, y=nr_firms)) + 
  geom_bar(stat = "identity", color="black", fill=colors[2]) +
  xlab(paste0("Country of origin (for ", mne_limit, "+ employee firms)")) +
  ylab("Number of foreign owned firms") +
  #xlim(0, 105) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=6), axis.title=element_text(size=20))

```


```{r}
# coagglomeration MNEs
mne_coagg_table <- construct_coagglomeration_table(mne_limited,
                                min_nr_firms_indreg = 10,
                                min_nr_regions_ind = 2,
                                min_nr_ind_reg = 2,
                                region_col,
                                industry_col)
```

```{r}
# coagglomeration plots
p1 <- ggplot(mne_coagg_table, aes(x = coagglomeration)) +
  geom_histogram(bins=30, , color="black", fill=colors[2]) +
  xlab("Coagglomeration") +
  ylab("Frequency") +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

p2 <- ggplot(mne_coagg_table, aes(x = coagglomeration)) +
  geom_histogram(bins=30, , color="black", fill=colors[2]) +
  xlab("Coagglomeration") +
  ylab("Frequency") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

(p1 + p2)
```


Manufacturing focus -- NACE C10 -- NACE C32.9.9

```{r}

cdf$nace3d <- as.numeric(cdf$nace3d)
manu_df <- subset(cdf, (nace3d > 100) & (nace3d < 330))

firm_info$nace3d_char <- as.numeric(firm_info$nace3d)


```






