---
title: "OPTEN coagglomeration and MNEs"
output: html_notebook
---

developed by sandorjuhasz

```{r, results=FALSE, message=FALSE}
source("../scripts/function_collection.R")
library(data.table)
library(dplyr)
options(dplyr.summarise.inform = FALSE)
library(mefa4)
library(ggplot2)
library(ggraph)
library(patchwork)
library(cowplot)


# OPTEN data
firm_info <- fread("../data/opten-dataset/mta_cegalap.csv", encoding='Latin-1')

# geo categories
geo_data <- fread("../data/iranyitoszamok_BE.csv")

# transaction data
tr_df <- fread("../data/industry_industry_table_nace3d.csv", sep=";")

# key parameters
colors <- c("#e9c46a", "#264653")
region_col <- "jaras"
industry_col <- "nace3d"

```


**Less than 5 digit NACE codes seem to be incorrect**

made corrections by checking 'fotev_nev' and 'fotev_kod'

```{r}
# generate 3-digit NACE codes -- NO leading zeros and many NAs
firm_info <- subset(firm_info, is.na(fotev_kod)==0)
firm_info$nace3d <- ifelse(nchar(firm_info$fotev_kod)==5,
                           substr(firm_info$fotev_kod, 1, 3),
                           substr(firm_info$fotev_kod, 1, 2))

# companies dataframe with key columns
cdf <- firm_info %>%
  select(oo_cegj_sz, hely, irsz, nace3d, letszam_besz18) %>%
  subset(is.na(irsz) == 0 & is.na(nace3d) == 0) %>%
  subset(letszam_besz18 >= 2) %>%
  dplyr::rename(emp = letszam_besz18) %>%
  data.table()

# join location info
cdf <- merge(
  cdf,
  unique(select(geo_data, irsz, jaras, megye)),
  by = "irsz",
  all.x = TRUE,
  all.y = FALSE) %>%
  subset(is.na(jaras) == 0)

# add industry, region and industry-region level attributes for future filters
cdf <- cdf %>%
  group_by(nace3d, jaras) %>%
  mutate(nr_firms_indreg = n_distinct(oo_cegj_sz),
         total_emp_indreg = sum(emp)) %>%
  group_by(nace3d) %>%
  mutate(nr_firms_ind = n_distinct(oo_cegj_sz),
         total_emp_ind = sum(emp),
         nr_regions_ind = n_distinct(jaras)) %>%
  group_by(jaras) %>%
  mutate(nr_firms_reg = n_distinct(oo_cegj_sz),
         total_emp_reg = sum(emp),
         nr_ind_reg  = n_distinct(nace3d)) %>%
  data.table()

```


**Issue -- MAV / Tesco / other HUGE companies**

check plants table, hopefully we can filter out firms with 100+ plants


**FILTERS**

min 10 firms per industry-region -- AND -- min 2 regions per industry -- AND -- min 2 industries per region


```{r}
# introduce filters
coagg_input <- subset(cdf, (nr_firms_indreg >= 10) & (nr_regions_ind >= 2) & (nr_ind_reg >= 2))

# constructing coagglomeration table
indreg_mat <- create_indreg_matrix(coagg_input, region_col, industry_col)
EGK_mat <- EGK_coagglomeration(indreg_mat)
coagg_table <- Melt(EGK_mat) %>% data.table()
colnames(coagg_table) <- c("ind1", "ind2", "coagglomeration")

# remove self loops and make it undirected
coagg_table$ind1 <- as.character(coagg_table$ind1)
coagg_table$ind2 <- as.character(coagg_table$ind2)
coagg_table <- subset(coagg_table, ind1 < ind2)

```


```{r, warning=FALSE}
# coagglomeration plots
p1 <- ggplot(coagg_table, aes(x = coagglomeration)) +
  geom_histogram(bins=30, , color="black", fill=colors[2]) +
  xlab("Coagglomeration") +
  ylab("Frequency") +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

p2 <- ggplot(coagg_table, aes(x = coagglomeration)) +
  geom_histogram(bins=30, , color="black", fill=colors[2]) +
  xlab("Coagglomeration") +
  ylab("Frequency") +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))

(p1 + p2)
```

**coagglomeration issues**

237 : Cutting, shaping and finishing of stone\
383 : Materials recovery

663 : Fund management activities \
701 : Activities of head offices 

351 : Electric power generation, transmission and distribution \
822 : Activities of call centres 


```{r}
arrange(coagg_table, desc(coagglomeration))
```

```{r}
cdf
```





**transaction data**


```{r}
# manipulation
tr_df$ind1 <- as.character(tr_df$ind1)
tr_df$ind2 <- as.character(tr_df$ind2)
#tr_df <- subset(tr_df, ind1 < ind2)

idf <- merge(
  coagg_table,
  select(tr_df, ind1, ind2, nr_trans),
  by = c("ind1", "ind2"),
  all.x = TRUE,
  all.y = FALSE
)

```


```{r}
limited_idf <- subset(idf, nr_trans >= 5)

ggplot(limited_idf, aes(x=coagglomeration, y=nr_trans)) +
  geom_point(size=5, color=colors[1], alpha=0.8) +
  #geom_smooth(method=lm, se=TRUE, linetype="dashed", color="black") +
  xlab("Coagglomeration") +
  ylab("Number of transactions") +
  #ylim(0, 1800) +
  #scale_x_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  scale_y_log10(labels = scales::trans_format("log10", scales::math_format(10^.x))) +
  theme_cowplot(12) +
  theme(axis.text = element_text(size=15), axis.title=element_text(size=20))
```


Skill relatednesss -- ADD

